\documentclass[11pt,twoside,letterpaper]{article}
\usepackage[margin=0.5in]{geometry}
% preamble - anything that is set before \begin{document}

\title{VGCMD Control Sheet}
\author{Ryan Pili}

\begin{document}

\maketitle

\section*{Control Sheet}
\flushleft
\begin{enumerate}
	\item Setup Computer.
		\begin{enumerate}
			\item Start in order: OBS, Audacity, Overcooked! 2, Zoom.
			\item Start meeting on Zoom and check AutoSizer is active
			\item Prepare Tutorial Level. .
		\end{enumerate}
	\item Once participant(s) walk(s) in: 
			\begin{itemize}
				\item One runner: Welcome, sign-in, consent.
				\item One runner: Start recording on OBS and Audacity -- \textbf{make sure waveform is recording on Audacity.}
			\end{itemize}
	\item Begin Tutorial.
		\begin{itemize}
			\item Instructions:
			\item ``You are going to be playing a video-game with another participant'' 
			\item Depending on condition: ``You will start with being able to see / not being able to see your partner. They will also be able / not be able to see you.''
				\begin{itemize}
					\item Place cardboard depending on condition.
				\end{itemize}
			\item ``Regardless, througout the experiment the webcam will be recording you for later analsys, no researchers will be watching your feed live.''
			\item ``We're going to start with a tutorial to intruduce you to the game, a sheet with the keyboard controls is presented, and I'd like to stress that you can emote to your parter by pressing E and an arrow key.''
			\item ``Please introduce yourself to your partner and begin when you're both ready''
		\end{itemize}
	\item Continue with First Condition.
		\begin{itemize}
			\item ``Any questions before we continue?''
			\item Setup the first level of the counter-balance
			\item ``Begin whenever the both of you are ready, and knock on the door when you're done.''
			\item Continue for the next 3 - 4 levels. 
			\item ``For blocks 6 - 10, you will be familiarized with the complex tone. For blocks 6 - 10: Odd trials will contain \textbf{no complex tone} and event trials will \textbf{contain a complex tone}.''
			\item ``No high tone will be presented for blocks 6 - 10''
			\item ``This is not a \textbf{testing phase} but a \textbf{familiarization phase}. Focus on learning the sounds of the different tones -- a green box will highlight the correct answer.''
			\item ``There will be very good instructions so make sure to \textbf{read them completely and carefully.}'' 
			\item ``I'll stay in and watch your \textbf{first block} in case you have any questions.'' 	
		\end{itemize}	
	\item Start first condition.
	\item Start second condition.
	\item Post-experiment survey.
		\begin{itemize}
			\item Can be found in:
				\begin{itemize}
					\item Kawamoto Drive
					\item FireFox Bookmarks
					\item Slack
				\end{itemize}
		\end{itemize}
	\item Prepare for next participant.
		\begin{itemize}
			\item Check \textbf{path} and \textbf{counterbalance}
				\begin{itemize}
					\item You need to remove \textasciitilde\textbackslash audab\textbackslash{} and all subfolders from the path.
					\item After, you can start from the top again without issues.
				\end{itemize}
			\item Prepare Hearing Test
		\end{itemize}	
\end{enumerate}

\section*{General Instructions}
\begin{itemize}
	\item Feel free to hold this with you and read off of it -- no need to memorize. It also really helps cut down on differences between participants if you say the exact same thing everytime.
\end{itemize}
\section*{Trouble Shooting}
\begin{itemize}
	\item Shadowing
\end{itemize}
\end{document}

